This section will describe how the communication between the \gls{rs} system and the \gls{astep} system is performed, and how features from the \gls{astep} API are used to achieve the desired functionality.

In the second sprint the \gls{rs} system was designed to consist of three parts: The \gls{rs} app, the \gls{rs} server, and the \gls{astep} system.
As the \gls{astep} system has evolved, small redesigns to the \gls{rs} system design are necessary.

The \gls{astep} API is, as described in Section \ref{ssec:communicationwithastep}, a REST API. 
This means that all API calls are done through HTTP requests\footnote{Overview of all the HTTP-request available in \gls{astep} can be found at \url{http://www.astep.cs.aau.dk/}}.

There are a number of API functions available through \gls{astep}, as previously stated in Table \ref{tab:sprint2-api}, but the \gls{rs} system will only be using a subset of the features: Routes and Users.
These are utilized to send gathered routes to \gls{astep}, and to create and edit users.
Because there are restrictions regarding user information sharing in \gls{astep}, it is also necessary to allow \gls{rs} to access the data from the \gls{astep} server for its users.

There are two ways of resolving user data sharing using the API.
The first solution is to create a group for all the \gls{rs} users, and the second is to create one administrating \gls{rs} user that has an access edge to every \gls{rs} user in \gls{astep} system.
The following paragraphs will elaborate the alternatives.

\paragraph{Groups}\\ 
Groups in the \gls{astep} system exist to allow users to gain access to each others data.
This could be utilized by making a \gls{rs} group in which all \gls{rs} users are included.
An issue with this solution is that all users have granted all other users access to their own location data. 
The solution allows a malicious programmer to create a program that either copies or edits the locations of all users of the \gls{rs} app.
The intruder would only need a registered \gls{rs} user and would thereby be included in the group.

\begin{figure}[h]
	\centering
	\begin{tikzpicture}
		\path[fill=red!30] (0:0cm) circle (2cm);
		\path[fill=green!30] (57:1.75cm) circle (1.3cm);
	
		\begin{scope}
			\clip(57:1.75cm) circle (1.3cm);
			\path[fill=red!30!green!30] (0:0cm) circle (2cm);
		\end{scope}
		
		\node at (0,	0) 		{$U_{\gls{rs}}$};
		\node at (0.8,	0.63) 	{$U_1$};
		\node at (0.1,	1.4)	{$U_2$};
		\node at (1.87,	1.4) 	{$U_3$};
		\node at (-1.2,	-0.3)	{$U_4$};
		\node at (0.7,	-1.2) 	{$U_5$};
		\node at (1.53, -0.84) 	{$U_6$};
	\end{tikzpicture}
	\label{fig:astepgroup}
	\caption{How the \gls{rs}-system would use groups. In the red group (the red circle) all users in that group can see all data from other users in the same group.}
\end{figure}

\paragraph{Edges}\\ 
Edges work in a similar way to groups, but only allowing access from one user to another.
Using the same method of establishing communication as with the groups we create a \gls{rs} user and creates a edge from that user to every user in the \gls{rs} system.
This way it is only when the \gls{rs} system uses its own user it is allowed to access data from the users.

\begin{figure}[h]
	\centering
	\begin{tikzpicture}
		
		\node (r) {$U_{\gls{rs}}$};
		\node[below of=r] (1) {$U_1$};
		\node[right of=1](2) {$U_2$};
		\node[left of=1] (4) {$U_4$};
		\node[right of=2] (5) {$U_5$};
		\node[left of=4] (6) {$U_6$};
		
		\draw[->] (r) -- (1);
		\draw[->] (r) -- (2);
		\draw[->] (r) -- (4);
		\draw[->] (r) -- (5);
		\draw[->] (r) -- (6);
		
		\draw[->] (1) -- (4);
	\end{tikzpicture}
	\label{fig:astepgroup}
	\caption{How the \gls{rs}-system would work with edges.}
\end{figure}

This means that edges can provide the same benifits without opening the same security flaws.
Therefor the edges is determined to be the superior system.

A  overview of every API calls, as of sprint 3, required by the \gls{rs}-system can be seen on Table \ref{tab:asteprequests}.

\begin{table}[h]
	\centering
	\scriptsize
	\begin{tabular}{l l l}
		Path & Method & Description\\\midrule
		/locations/outdoor/\{username\}/routes & POST & Send a route to the \gls{astep} server\\
		/locations/outdoor/\{username\}/routes/match & GET & Match all new routes\\
		/users & POST & Create a new user\\
		/users/\{username\}/outUsers & POST & Request a new out user\\
		/users/\{username\}/outUsers/\{specifiedUsername\} & PUT & Accept out user\\
		/users/\{username\}/token & GET & Get the current valid token for a user
	\end{tabular}
	\label{tab:asteprequests}
	\caption{}
\end{table}

In sprint 2 it was also decided to created a user through the \gls{rs} server, this have been changed to simplify the implementation.
When a user registers in the app an API call will be issued to the \gls{astep} API directly from the app where before this was done through the \gls{rs} server. 
The username and the additional information such as phone number and full name are still transfered to the \gls{rs} server for storing.