\section{Design}
If you've been in Alaska less than a year you're a Cheechako. We spend so much of our life looking - but never seeing. Fluff that up. I can't think of anything more rewarding than being able to express yourself to others through painting.

We need dark in order to show light. Let's have a little bit of fun today. This painting comes right out of your heart. Even trees need a friend. We all need friends. Use absolutely no pressure. Just like an angel's wing. Talent is a pursued interest. That is to say, anything you practice you can do.

It looks so good, I might as well not stop. It's almost like something out of a fairytale book. Put it in, leave it alone. If there's two big trees invariably sooner or later there's gonna be a little tree. The only thing worse than yellow snow is green snow.

Painting should do one thing. It should put happiness in your heart. Let's do that again. We artists are a different breed of people. We're a happy bunch. Let that brush dance around there and play. That's what makes life fun. That you can make these decisions. That you can create the world that you want.

Let's make a nice big leafy tree. A little happy sunlight shining through there. And just raise cain. We have a fantastic little sky!

In this world, everything can be happy. Imagination is the key to painting. Nature is so fantastic, enjoy it. Let it make you happy. It is a lot of fun. Look around, look at what we have. Beauty is everywhere, you only have to look to see it. I'll go over the colors one more time that we use: Titanium white, Thalo green, Prussian blue, Van Dyke brown, Alizarin crimson, Sap green, Cad yellow, and Permanent red.

Go out on a limb - that's where the fruit is. If I paint something, I don't want to have to explain what it is. These trees are so much fun. I get started on them and I have a hard time stopping. Let's go up in here, and start having some fun It's a good way of getting rid of all your anxieties and hostilities.

