\subsection{Background Service}
The \texttt{JobScheduler} was chosen as the scheduler for managing the background service in Section \ref{ssec:periodictasks}.
The \texttt{JobScheduler} works by scheduling Intents, that are operations to be performed. 
An \texttt{Intent} that is not yet executed, is called a \texttt{PendingIntent}.
When a \texttt{PendingIntent} is finally executed, variables in the systems may have been changed, hence the context might not be the correct, therefore a \texttt{PendingIntent} also requires a reference to the context when it was created.
This is performed to ensure that permissions given to the app are still available when the \texttt{job} is executed.
A \texttt{job} is a \texttt{PendingIntent} as described in Section \ref{ssec:periodictasks} and a set of requirements for when the intent should be executed.

When a job is handed to the \texttt{JobScheduler}, information about the nature of the scheduling is also provided.
This includes requirements that needs to be fulfilled before the job can run, how often the job should be executed, and how precise the timing of the job should be.

\begin{lstlisting}[language=Java, label=jobScheduler, caption=The implementation of jobScheduler.]
JobScheduler jobScheduler = (JobScheduler) getSystemService(JOB_SCHEDULER_SERVICE);
JobInfo.Builder builder = new JobInfo.Builder(1, new ComponentName(getPackageName(), RideShareService.class.getName()));
builder.setPeriodic(120000);
int response  = jobScheduler.schedule(builder.build());	
\end{lstlisting}

Listing \ref{jobScheduler} presents the implementation of \texttt{jobScheduler} in the \texttt{MainActivity} of the app.

In the app, the jobScheduler is implemented as an extension to the \texttt{JobService} class which provides the required interface for the \texttt{JobScheduler} called RideShareService.
The class reroutes the call by the \texttt{JobScheduler} to a \texttt{Handler} class.
This \texttt{Handler} class, as described by the official documentation \cite{handler}, allows the service to send a runnable object to the threads message queue.


The implementation makes the location gathering be performed as a background service every two minutes.
As covered in Section \ref{ssec:loctrack} this interval is temporary, and will serve to test the implementation, until further experience is gathered regarding optimizing the task frequency.


