\section{Implementation}
Every day I learn. You're meant to have fun in life. Pretend you're water. Just floating without any effort. Having a good day. I really believe that if you practice enough you could paint the 'Mona Lisa' with a two-inch brush. Automatically, all of these beautiful, beautiful things will happen.

Anything you want to do you can do here. Nice little clouds playing around in the sky. Just go back and put one little more happy tree in there.

And I know you're saying, 'Oh Bob, you've done it this time.' And you may be right. Now it's beginning to make a little sense. Tree trunks grow however makes them happy. Everyone needs a friend. Friends are the most valuable things in the world. This is unplanned it really just happens. This is a happy place, little squirrels live here and play.

Let's have a happy little tree in here. I really recommend you use odorless thinner or your spouse is gonna run you right out into the yard and you'll be working by yourself. The only thing worse than yellow snow is green snow. Think about a cloud. Just float around and be there. You better get your coat out, this is going to be a cold painting. Get tough with it, get strong.

You are only limited by your imagination. The more we do this - the more it will do good things to our heart. Son of a gun. Just a happy little shadow that lives in there. Let all these things just sort of happen. Put it in, leave it alone.

There isn't a rule. You just practice and find out which way works best for you. Let that brush dance around there and play. The first step to doing anything is to believe you can do it. See it finished in your mind before you ever start. You don't have to be crazy to do this but it does help. These things happen automatically. All you have to do is just let them happen.

Isn't it great to do something you can't fail at? Almost everything is going to happen for you automatically - you don't have to spend any time working or worrying. Use what happens naturally, don't fight it. It's a super day, so why not make a beautiful sky?

