\chapter*{Preface\markboth{Preface}{Preface}}\label{ch:preface}
\addcontentsline{toc}{chapter}{Preface}
The purpose of this report is to document the development and work process of the semester project performed the spring of 2016 by our group, SW605F16.
This project was developed as part of the multi-group project \gls{astep}.
Throughout the project, we gained experience working with Android, Java Sockets, Http Requests, and multi-group project collaboration.

The developed solution consists of three parts: an app, a server and an \gls{astep} integration.
These cooperate and serve to provide app users with automatic ride sharing suggestions for their recurring driven routes, as a mean to reduce traffic, emissions and time.

We would like to thank Davide, our supervisor, for his work and support throughout the project, and Bin Yang for the multi-group project suggestion of \gls{astep}.


\iffalse
This report has been written in May 2000 in a four–week project at the IT
University of Copenhagen under the supervision of . . . . We thank John
Doe for assistance with the program for handling TIFF–images.

During the project, we developed a Java–program for analysis of microscope
images of lactic acid bacteria. The program analyses a TIFF file that
is produced by a digital camera that in turn is connected to a microscope.
It finds the contours of all bacteria above a certain size in the image, and
prints these contours to a file in REG format. Files in REG can then be given
as input to the standard program BactEdit from Yoyodyne Corp., and one
therefore saves the tedious manual drawing of the bacteria’s contours in
BactEdit
\fi

\vspace{\baselineskip}\hfill Aalborg University, \today
\vfill\noindent
\begin{minipage}[b]{0.45\textwidth}
 \centering
 \rule{\textwidth}{0.5pt}\\
  Bjørn E.Opstad\\
 {\footnotesize <bopsta13@student.aau.dk>}
\end{minipage}
\hfill
\begin{minipage}[b]{0.45\textwidth}
 \centering
 \rule{\textwidth}{0.5pt}\\
  Claus W. Wiingreen\\
 {\footnotesize <cwiing13@student.aau.dk>}
\end{minipage}

\vspace{3\baselineskip}
\noindent
\begin{minipage}[b]{0.45\textwidth}
 \centering
 \rule{\textwidth}{0.5pt}
  Mathias C. Mikkelsen\\
 {\footnotesize <mcmi13@student.aau.dk>}
\end{minipage}
\hfill
\begin{minipage}[b]{0.45\textwidth}
 \centering
 \rule{\textwidth}{0.5pt}
  Morten Pedersen\\
 {\footnotesize <morped13@student.aau.dk>}
\end{minipage}