\chapter*{Summary}
During this semester, we have collaborated with nine other groups on the startup of a new multi-group project with the goal of developing a platform for spatial and temporal data management called aSTEP. The system was also required to be developed with accompanying apps. Our task in the multi-project was to develop an application that would utilize the aSTEP system API and database.

We designed and developed an application with the goal of automatically finding ridesharing candidates based on tracking of the application users commutes. The solution was also designed to automatically detect which routes a user drove was reoccurring in a weekly basis. If a stable route is found it is then compared with every other stable route in the aSTEP system to find a match. If a match between two users were found, the matches would then be displayed in the application with a score from 0 to 100.

% Solution
The developed solution is fulfilling our highest prioritized requirements, but still has potential for improvement. There are requirements we have written that are not yet fulfilled during the development process and therefore not implemented. The app does, however, suffice as a proof of concept for the aSTEP system and as a foundation for further development. 

% aSTEP
The aSTEP system was developed to a stage where the API and database had enough functionality to support applications that would store locations, routes, and compute ride matches. There exists a satisfying user management system, where users can be created and managed. These users can be utilized in the applications to ensure correct authentication for the different API calls.

% Collaboration
We have been collaborating with the other aSTEP groups in multiple degrees and with different motivations. The collaboration with the FriendFinder app group was superficial, and only to vaguely agree on the visual UI design scheme. 
However, we mostly collaborated with the OD group, as they were responsible for handling the location input and implementation of the route matching algorithm on our behalf in the aSTEP system. 
The user management group was also collaborated with, as they were responsible for the user management functionality in the aSTEP system. We discussed multiple types of functionality and privacy concerns with them, and the other app groups were also involved, as the aSTEP system should be modular and usable for multiple app types.

% Algorithm
For this project to work, an algorithm that solved our problem was necessary. The report cover our logic behind the algorithm and how we worked together with the group that implemented it to test it.