\section{Conclusion}
% meta and contin. of introduction
The \gls{rs} solution, consisting of an Android application accommodated by an assisting server, utilizing the \gls{astep} system that was developed in this project, and this section documents the conclusion of the project.


% conclusion on working process and cooperation
The \gls{astep} system was developed concurrently with the \gls{rs} solution, and both systems were dependent upon each other to be expedient.
The parallel development was influencing the development of the \gls{rs} solution, but also gave the possibility of establishing requirements for the \gls{astep} system.
The cooperation development process gave challenges as the other parts of the system were continuously altered, but a stable design was finally achieved and lead to a system that was functional.


% conclusion on the solution
The solution fulfills the established requirements regarding both functionality and cooperation with the other semester project groups, as stated in the test in Section \ref{sec:s4test}.
There is improvement potential for the solution, but the 'Must have' requirements are met, and the solution is acceptable in this regard.


% conclusion on the problem statement
The project was aimed at solving the problem statement, as defined in Section \ref{sec:probstat}:

{\addtolength{\leftskip}{10mm}\addtolength{\rightskip}{10mm}\noindent\hrulefill\it
	
	\noindent How can one design and develop an app that automatically suggests ride sharing companions, based on common locations in origin and destination, utilizing the \gls{astep} platform? 
	
	\noindent\hrulefill
	
}


The problem statement has been the initiating factor of the development process, and was decomposed into multiple requirements.
While the 'Must have' requirements are fulfilled, there are still remaining requirements regarding parts of the solution that are not completed.
However, the 'Must have' requirements were sufficiently covering the minimum level of functionality, and hence the problem statement is fulfilled and the solution is considered successfully accomplished.


% final conclusion
The semester project, solution, and the multi-group project solution lays the foundation for a potentially comprehensive location based service for both indoor and outdoor positioning.
Although the \gls{rs} app could benefit from a user interface redesign in terms of aesthetics, it solves the problem statement and can be applied in the real world.
