\chapter{Evaluation}
This chapter contains the reflection, conclusion and future work.
First we will reflect upon the project, with regards to both the internal group work and the multi-group experience.
Thereafter, we conclude on our work for the project and solution.
Last, we describe our thoughts about potential of the solution and possible future work.

\section{Reflection}
This section contains our reflection of the different project aspects.
First we reflect on our own project, then the multi-group project is reflected upon and evaluated.

\subsection{Project Reflection}
% project conten and system design/implementation
The system design was influenced by the \gls{astep} progression during the development as the system relied on \gls{astep}.
Throughout the project, there were multiple changes in the \gls{astep} system, which had different impacts on our project.
Most significant was the change from \gls{astep} storing supplemental user information, such as e-mail address, to not storing anything other than username and password.
The system design could have been better and there would have been more time for implementation if the final \gls{astep} system design had been established from the beginning.

% project process and work distribution
The implementation was successful and dynamic, adjusting to changes made in the \gls{astep} project and our own tests performed throughout the sprints, in accordance with the iterative method.
All group members were included in every part of the project.
Each member had a possibility to discuss the individual parts, despite being assigned to another part during that time period.
The tasks were evenly distributed on the group members, and more complex tasks were assigned to multiple members when necessary.

% project work load
We were ambitious with the extent of the project, therein objectives regarding custom user settings of having a car or not, despite the project leader Bin Yang proposed low ambition levels and just making a working basis.
Our ambition level is reflected in the requirement specification, and as seen in the acceptance test in Section \ref{sec:s4test}, only the 'must have' requirements are fulfilled.
The workload during the project has been high while there has been a joint attitude of making the solution as high quality as possible.
The ambition level and the established requirement specification together with unexpected task completion durations have caused delays during the sprints so that actual deadlines were sometimes not met.
This happened during sprint 2 and 3, where our internal deadline would extend two weeks past the multi-group project deadlines.
The missed deadlines had no effect on the \gls{astep} project but made our own scheduling harder to meet.

% realism comment
The solution development could have been more realistic if we had potential costumers to request features of us.
This would apply more pressure to and reliance on the group collaborations and flow of information within the \gls{astep} project.

% boom?
The \gls{rs} app is a functional prototype, and is seen as a success since it utilizing the \gls{astep} system.

\input{sections/groupeval.tex}
